This PDF is a Git Repository\\Containing its Own \LaTeX\ Source\\and a Copy of Itself

### 2017-05-07 article.tex
Added an ending

@@

>>>>

“Thus—thus, my fellow-labourers and associates in this great harvest of our learning, now ripening before our eyes; thus it is, by slow steps of casual increase, that our knowledge physical, metaphysical, physiological, polemical, nautical, mathematical, aenigmatical, technical, biographical, romantical, chemical, and obstetrical, with fifty other branches of it, (most of 'em ending as these do, in ical) have for these two last centuries and more, gradually been creeping upwards towards that Akme of their perfections, from which, if we may form a conjecture from the advances of these last seven years, we cannot possibly be far off.”

Excerpt From: Laurence Sterne. “The Life and Opinions of Tristram Shandy, Gentleman.” iBooks.

@@

{\fontfamily{jkpvos}\selectfont\begin{center}
\begin{minipage}{0.8\hsize}\small
Thus=---thus=, my fellow-labourers= and associates= in this great harvest of our learning, now ripening before our eyes=; thus it is=, by slow steps= of casual increase, that our knowledge physical, metaphysical, physiological, polemical, nautical, mathematical, \ae{}nigmatical, technical, biographical, romantical, chemical, obstetrical, and polyglottical, with fifty other branches= of it, (most of 'em ending as= these do, in ical) have for these four last centuries= and more, gradually been creeping upwards= towards that Akme of their perfections=, from which, if we may form a conjecture from the advances= of these last \thepage~pages=, we cannot possibly be far off.
\end{minipage}
\end{center}}
